EE454 Project 1 Report

### 2015-09-23 p1/report/latex/draft.tex
f

\documentclass[11pt,english]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage[toc,page]{appendix}
\graphicspath{ {../} }

@@

Included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.

\section{Performance Evaluation}
\subsection{Results}
	The following results were the outcome of classifying images as the class associated with the highest probability in the probability vector.
\begin{center}
	\includegraphics[scale=0.8]{confusionmatrix}
	~\\~\\

@@

\begin{center}
	\includegraphics[scale=0.7]{confsurf}
	~\\~\\
\end{center}
\textbf{Discussion:}

@@

@@

\section{Member Contributions}

>>>>

\documentclass[11pt,english]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage[toc,page]{appendix}
\usepackage{titlesec}
\graphicspath{ {../} }

\newcommand{\sectionbreak}{\clearpage}

@@

Intermediate output generated by the CNN is included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.

\section{Performance Evaluation}
\subsection{Results}
	The following results were the outcome of classifying images as the class associated with the highest probability in the probability vector.
\begin{center}
	\includegraphics[scale=0.7]{confusionmatrix}
	~\\~\\

@@

\begin{center}
	\includegraphics[scale=0.6]{confsurf}
	~\\~\\
\end{center}
\textbf{Discussion:}

@@

~\\~\\
\noindent
Note: All of the exploratory images we used were either taken by us or were taken from Google Images.

@@

\section{Member Contributions}
	Overall the contributions made form each team member were pretty even. Whenever the team met to work on the project most of the team members were in attendance. Everyone who was in attendance at each team meeting attempted to work on a different piece of the project to ensure that we were making steady progress. The coding was not split up evenly as one team member did not attend the initial meeting and as a result he missed most of the actual coding and basically all of the design decisions. We attempted to split the report up evenly, but as the deadline approached scheduling meetings became difficult and some individuals were unavailable to work on the report. In conclusion, the work was not split up evenly among our four group members, but everyone attempted to contribute.
